### 2023-06-20 bachelorthesis/34-restartscript.tex
#39: Bachelor thesis finished

As script language \texttt{python} was chosen because of its simple syntax and the variety of tools compatible with the \texttt{bash} shell. \texttt{bash} was also considered, but after some issues occurred regarding the mechanism to check wether a file exist or not, \texttt{python} was selected. Furthermore, the script uses the standard \texttt{python3} library and is therefore executabe with any \texttt{python3} enviroment.

The script was named \texttt{slurm\_monitor.py} to indicate that this script works with the \texttt{Slurm} resource manager. The source code was pushed to the gkw repository on BitBucket \cite{slurmmonitor} or can be found in Appendix \ref{append:slurmcode}

@@

The restart script has several features which can be used via the command line interface as parser options. The following features with the corresponding parser option were implementing:
\begin{itemize}
    \item \textbf{\textcolor{red}{!Required!}} Set job name not longer than 8 characters to identify simulation\\
          \texttt{-j [JOBNAME], -\/-job-name [JOBNAME]}
    \item Can be started from everywhere with simulation folder path\\
          \texttt{-d [DIRECTORY], -\/-dir [DIRECTORY]~~~~~~~~~~~~~(default=cwd)}
    \item Creates jobscript file with defined content (variable \texttt{jobscriptContent})\\
          \texttt{-\/-jobscript [JOBSCRIPTFILE]~~~~~~~(default=jobscript-create)}\\
          \texttt{-\/-nodes [NODES]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=3)}\\
          \texttt{-\/-ntask-per-node [TASKS]~~~~~~~~~~~~~~~~~~~~~~~~(default=32)}\\
          \texttt{-\/-walltime [WALLTIME]~~~~~~(d-hh:mm:ss)~(default=0-24:00:00)}
    \item Start/Restarts simulation until job criteria is suffused\\
          \texttt{-n [TIMESTEPS]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,\,(default=10000)}\\
          \texttt{-\/-restartfile [RESTARTFILE]~~~~~~~~~~~~~~~~(default=FDS.dat)}
    \item Makes backup after each run before Restart and Restore files after failed run\\
          Quicklinks: \texttt{local} (simulation folder), \texttt{home} (home folder) \\
          \texttt{-b [LOCATION], -\/-backup [LOCATION]~~~~~~~~~~~\,(default=None)}
    \item Reset option after run fails and dump files were written\\
          (rely on \texttt{h5py}, \texttt{pandas} and \texttt{numpy} which get installed by the script itself)\\
          \texttt{-r, -\/-reset~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
    \item Creates status file with current status and progress bars and updates it dynamically\\
          \texttt{-\/-statusfile [STATUSFILE]~~~~~~~~~~~~~~~(default=status.txt)}
    \item Set form of the output table in status file\\
          Options: fancy (round box), universial (crossplattform), None (No frame)\\
          \texttt{-\/-format [FORMATTABLE]~~~~~~~~~~~~~~~~~~~~~~~~(default=None)}
    \item Sends mail at the beginning, end and restart with status file as attachment\\
          (\texttt{mailx} other equivalent has to be installed, look into \texttt{send\_mail} function for more info)\\
          \texttt{-\/-mail [MAILADDRESS]~~~~~~~~~(mail@server.de)~(default=None)}\\
          \texttt{-\/-restart-mail ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Kills monitoring process by using the \texttt{PID} number\\
          \texttt{-\/-kill~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Set sleep interval after which the status of the current simulation should be checked\\
          \texttt{-\/-refresh-rate [SLEEPTIME]~~~~~~~~~~~~~~~~~~~~~(default=300)}
    \item Print output of status file table to console\\
          \texttt{-v, -\/-verbose~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
\end{itemize}
All boolean parameters are switches, i.e., the praser option only changes the value from \texttt{False} to \texttt{True}.

@@

As stated in Chapter \ref{sub:codeFeatures} the restart script is writing a status file with the current status and progress bars of the simulation. The output is formatted as a table and can be adjusted in its appearance with the \texttt{-\/-format} parser option [Chapter \ref{sub:codeFeatures}]. The output types written in the status file are listed in Tab. \ref{tab:statusTypes}. To each output the restart script writeesthe date, time and the duration of the monitoring additionally into the table. 
\begin{center}
    \captionsetup{type=table}
    \begin{tabular}{l | l}
        Type              & Information                                                                                     \\\hline
        \texttt{STARTING} & Start monitoring process or Start/Restart of simulation                                         \\
        \texttt{CONTINUE} & If the simulation has performed at least one run                                                \\\hline
        \texttt{CONTROL}  & Check the current time steps of the simulation                                                  \\
        \texttt{SUCCESS}  & Stop monitoring because the time steps condition has been fulfilled                             \\\hline
        \texttt{IMPORT}   & Modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} will be loaded                        \\
        \texttt{INSTALL}  & Script installs the modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} on the user level \\
        \texttt{CHECK}    & Required modules to use the reset option are already installed                                  \\\hline
        \texttt{WAITING}  & Simulation is pending in the queue of Slurm                                                     \\
        \texttt{RUNNING}  & Simulation is running on the server                                                             \\\hline
        \texttt{BACKUP}   & The script performs data backup to the predefined location                                      \\
        \texttt{RESTORE}  & The script reloads the data from the backup folder if errors occur                              \\
        \texttt{RESET}    & The simulation restes with the use of dump files                                                \\\hline 
        \texttt{ERROR}    & An error occur during monitoring                                                                \\
                          & Types:                                                                                          \\
                          & No executable (\texttt{gkw.x}), walltime, timeout, no config, \texttt{hdf5}, string error       \\
    \end{tabular}
    \captionof{table}{Output types in status file}
    \label{tab:statusTypes}
\end{center}

To continue, the status file has different style options, e.g., \texttt{fancy}, \texttt{universal} and \texttt{None} which are displayed in Fig. \ref{fig:statusStyle}. 
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
  ╭───────────────╮    +---------------+    ------------------
  │     fancy     │    |   universal   |           None
  ├───────────────┤    +---------------+    ------------------
  │               │    |               |    
  ╰───────────────╯    +---------------+    ------------------
\end{verbatim}
\captionof{figure}{Styles of output table in status file}
\label{fig:statusStyle}
\end{center}
In addition to that, it dynamically updates the progress of simulation to the end of the status file in form of a progress bar. The progress bar contains the current time step of the simulation in contrast to the required time steps and the progress of the run itself in seconds in relation to the wall time. It also contains the current output from \texttt{squeue}, if the simulation is running or pending, else the important information of the simulation. An example progress bar ist shown in Fig. \ref{fig:statusBar}.
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
 +------------------------------------------------------------+
 |  JOBID  NAME     USER ST    TIME NODES  NODELIST(REASON)   |
 | 970455 3x1.5 bt712347 CG 3:16:01     3  r03n03,r05n[15-16] |
 +------------------------------------------------------------+
 | PROGRESS  [===================>.....]  ( 80%)  20000/25000 |
 | RUN 13    [===>.....................]  ( 13%)  11462/86400 |
 +------------------------------------------------------------+
\end{verbatim}
\captionof{figure}{Progress bar example}
\label{fig:statusBar}
\end{center}
The progress bar displays all important information at one glance. To boost productivity the following command is recommended:
\begin{lstlisting}
cd $DATA 
find . -name $STATUSFILENAME -exec tail -8 {} \;
\end{lstlisting}
which prints all progress bars of every simulation to the data folder. If one wants to see the complete status file change \texttt{tail -8} to \texttt{cat}.
An example status file is displayed in the Appendix \ref{append:status}.

>>>>

As script language \texttt{python} was chosen because of its simple syntax and the variety of tools compatible with the \texttt{bash} shell. \texttt{bash} was also considered, but after some issues occurred regarding the mechanism to check whether a file exist or not, \texttt{python} was selected. Furthermore, the script uses the standard \texttt{python3} library and is therefore executable with any \texttt{python3} environment.

The script was named \texttt{slurm\_monitor.py} to indicate that this script works with the \texttt{Slurm} resource manager. The source code was pushed to the GKW repository on BitBucket \cite{slurmmonitor} or can be found in Appendix \ref{append:slurmcode}

@@

The restart script has several features which can be used via the command line interface as parser options. The following features with the corresponding parser option were implementing:
\begin{itemize}
    \item \textbf{\textcolor{red}{!Required!}} Set job name not longer than 8 characters to identify simulation\\
          \texttt{-j [JOBNAME], -\/-job-name [JOBNAME]}
    \item Can be started from everywhere with simulation folder path\\
          \texttt{-d [DIRECTORY], -\/-dir [DIRECTORY]~~~~~~~~~~~~~(default=cwd)}
    \item Creates jobscript file with defined content (variable \texttt{jobscriptContent})\\
          \texttt{-\/-jobscript [JOBSCRIPTFILE]~~~~~~~(default=jobscript-create)}\\
          \texttt{-\/-nodes [NODES]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=3)}\\
          \texttt{-\/-ntask-per-node [TASKS]~~~~~~~~~~~~~~~~~~~~~~~~(default=32)}\\
          \texttt{-\/-walltime [WALLTIME]~~~~~~(d-hh:mm:ss)~(default=0-24:00:00)}
    \item Start/Restarts simulation until job criteria is suffused\\
          \texttt{-n [TIMESTEPS]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,\,(default=10000)}\\
          \texttt{-\/-restartfile [RESTARTFILE]~~~~~~~~~~~~~~~~(default=FDS.dat)}
    \item Makes backup after each run before Restart and Restore files after failed run\\
          Quicklinks: \texttt{local} (simulation folder), \texttt{home} (home folder) \\
          \texttt{-b [LOCATION], -\/-backup [LOCATION]~~~~~~~~~~~\,(default=None)}
    \item Reset option after run fails and dump files were written\\
          (rely on \texttt{h5py}, \texttt{pandas} and \texttt{numpy} which get installed by the script itself)\\
          \texttt{-r, -\/-reset~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
    \item Creates status file with current status and progress bars and updates it dynamically\\
          \texttt{-\/-statusfile [STATUSFILE]~~~~~~~~~~~~~~~(default=status.txt)}
    \item Set form of the output table in status file\\
          Options: fancy (round box), universial (crossplattform), None (No frame)\\
          \texttt{-\/-format [FORMATTABLE]~~~~~~~~~~~~~~~~~~~~~~~~(default=None)}
    \item Sends mail at the beginning, end and restart with status file as attachment\\
          (\texttt{mailx} other equivalent has to be installed, look into \texttt{send\_mail} function for more info)\\
          \texttt{-\/-mail [MAILADDRESS]~~~~~~~~~(mail@server.de)~(default=None)}\\
          \texttt{-\/-restart-mail ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Kills monitoring process by using the \texttt{PID} number\\
          \texttt{-\/-kill~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Set sleep interval after which the status of the current simulation should be checked\\
          \texttt{-\/-refresh-rate [SLEEPTIME]~~~~~~~~~~~~~~~~~~~~~(default=300)}
    \item Print output of status file table to console\\
          \texttt{-v, -\/-verbose~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
\end{itemize}
All boolean parameters are switches, i.e., the parser option only changes the value from \texttt{False} to \texttt{True}.

@@

As stated in Chapter \ref{sub:codeFeatures} the restart script is writing a status file with the current status and progress bars of the simulation. The output is formatted as a table and can be adjusted in its appearance with the \texttt{-\/-format} parser option [Chapter \ref{sub:codeFeatures}]. The output types written in the status file are listed in Table \ref{tab:statusTypes}. To each output the restart script writes the date, time and the duration of the monitoring additionally into the table. 
\begin{center}
    \captionsetup{type=table}
    \begin{tabular}{l | l}
        Type              & Information                                                                                     \\\hline
        \texttt{STARTING} & Start monitoring process or Start/Restart of simulation                                         \\
        \texttt{CONTINUE} & If the simulation has performed at least one run                                                \\\hline
        \texttt{CONTROL}  & Check the current time steps of the simulation                                                  \\
        \texttt{SUCCESS}  & Stop monitoring because the time steps condition has been fulfilled                             \\\hline
        \texttt{IMPORT}   & Modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} will be loaded                        \\
        \texttt{INSTALL}  & Script installs the modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} on the user level \\
        \texttt{CHECK}    & Required modules to use the reset option are already installed                                  \\\hline
        \texttt{WAITING}  & Simulation is pending in the queue of Slurm                                                     \\
        \texttt{RUNNING}  & Simulation is running on the server                                                             \\\hline
        \texttt{BACKUP}   & The script performs data backup to the predefined location                                      \\
        \texttt{RESTORE}  & The script reloads the data from the backup folder if errors occur                              \\
        \texttt{RESET}    & The simulation restes with the use of dump files                                                \\\hline 
        \texttt{ERROR}    & An error occur during monitoring                                                                \\
                          & Types:                                                                                          \\
                          & No executable (\texttt{gkw.x}), walltime, timeout, no config, \texttt{hdf5}, string error       \\
    \end{tabular}
    \captionof{table}{Output types in status file}
    \label{tab:statusTypes}
\end{center}

To continue, the status file has different style options, e.g., \texttt{fancy}, \texttt{universal} and \texttt{None} which are displayed in Fig. \ref{fig:statusStyle}. 
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
  ╭───────────────╮    +---------------+    ------------------
  │     fancy     │    |   universal   |           None
  ├───────────────┤    +---------------+    ------------------
  │               │    |               |    
  ╰───────────────╯    +---------------+    ------------------
\end{verbatim}
\captionof{figure}{Styles of output table in status file.}
\label{fig:statusStyle}
\end{center}
In addition to that, it dynamically updates the progress of simulation to the end of the status file in form of a progress bar. The progress bar contains the current time step of the simulation in contrast to the required time steps and the progress of the run itself in seconds in relation to the wall time. It also contains the current output from \texttt{squeue}, if the simulation is running or pending, else the important information of the simulation. An example progress bar is shown in Fig. \ref{fig:statusBar}.
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
 +------------------------------------------------------------+
 |  JOBID  NAME     USER ST    TIME NODES  NODELIST(REASON)   |
 | 970455 3x1.5 bt712347 CG 3:16:01     3  r03n03,r05n[15-16] |
 +------------------------------------------------------------+
 | PROGRESS  [===================>.....]  ( 80%)  20000/25000 |
 | RUN 13    [===>.....................]  ( 13%)  11462/86400 |
 +------------------------------------------------------------+
\end{verbatim}
\captionof{figure}{Progress bar example.}
\label{fig:statusBar}
\end{center}
The progress bar displays all important information at one glance. To boost productivity the following command is recommended:
\begin{lstlisting}
cd $DATA 
find . -name $STATUSFILENAME -exec tail -8 {} \;
\end{lstlisting}
which prints all progress bars of every simulation to the data folder. If one wants to see the complete status file change \texttt{tail -8} to \texttt{cat}.
An example status file is displayed in the Appendix \ref{append:status}.

### 2023-06-20 bachelorthesis/41-resolution.tex
#39: Bachelor thesis finished

At the beginning of this work the goal is to estimate the minimal resolution needed to run the simulation without numerical dissipation biasing the physical outcome. Numerical dissipation can therefore result to no formation of zonal flow structures, which cause an permanent turbulent state of the simulation. The goal behind this testing is to reduce \textbf{calculation time} and \textbf{costs} of the simulation. \\
Because of that, the criteria for the best resolution should be:
\begin{enumerate}
	\item[\textbf{(1)}] Subdued turbulence after \textbf{short} time periods
	\item[\textbf{(2)}] Stability for \textbf{long} time periods 
\end{enumerate}
and the following procedure will be applied for verification:
\begin{enumerate}
	\item Reduce only one number of grid points and look if criterias \textbf{(1), (2)} are satisfied
	\item Reduce to known minimum number of grid points to verify result in general.
\end{enumerate}

@@

Starting from the \enquote{Standard resolution with 6th order (S6)} [Tab. \ref{tab:resolutionBenchmark}] the first step is to reproduce the result of Ref. \citenum{Peeters2016} in Section IV. Note that, because of selected circular concentric geometry the used inverse background temperature gradient length is $\rlt = 6.0$ instead of $\rlt = 7.0$ which was used in Section IV of Ref. \citenum{Peeters2016} for $s$-$\alpha$ geometry. In Fig. \ref{fig:eflux-ns16-nvpar64-nmu9} the obtained data is similar to the results from Ref. \citenum{Peeters2016} with subdued turbulence after $\sim 3000\,R/\vth$.

\includegraphicsHere{S6_rlt6.0/boxsize1x1/Ns16/Nvpar64/Nmu9/S6_rlt6.0_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux.pdf}{
	Time trace of the heat conduction coefficient $\chi$ for $\rlt = 6.0$ for benchmark
}{fig:eflux-ns16-nvpar64-nmu9}{}

@@

\includegraphicsHere{Comparison/Gradient-Length/S6_rlt6.0-6.3_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux_comparison.pdf}{
	Time traces for $\rlt = 6.0$ and $\rlt = 6.3$ for benchmark
}{fig:eflux-gradient-length}{}

@@

\includegraphicsHere{Comparison/Resolution/Nvpar/S6_rlt6.0_boxsize1x1_Ns16_Nvpar16-32-48-64_Nmu9_eflux_comparison.pdf}{
	Time traces for reduced parallel velocity grid points $\Nvpar$
}{fig:eflux-ns16-nvpar16-32-48-64-nmu9}{}

@@

\includegraphicsHere{Comparison/Resolution/Nmu/S6_rlt6.0_boxsize1x1_Ns16_Nvpar64_Nmu6-9_eflux_comparison.pdf}{
	Time traces for reduced magnetic moment grid points $\Nmu$
}{fig:eflux-ns16-nvpar64-nmu6-9}{}

@@

\includegraphicsHere{Comparison/Resolution/Nmu/S6_rlt6.0_boxsize1x1_Ns16_Nvpar48_Nmu6-9_eflux_comparison.pdf}{
	Time traces for reduced magnetic moment grid points $\Nmu$
}{fig:eflux-ns16-nvpar48-nmu6-9}{}

@@

\includegraphicsHere{Comparison/Resolution/Ns/S6_rlt6.0_boxsize1x1_Ns12-16_Nvpar64_Nmu9_eflux_comparison.pdf}{
	Time traces for reduced magnetic field grid points $\Ns$
}{fig:eflux-ns12-16-nvpar64-nmu9}{}

@@

Together with the results of Chapter \ref{sub:reduceNvpar}, \ref{sub:reduceNmu} and \ref{sub:reduceNs} the final resolution used in the upcoming simulations is displayed in Tab. \ref{tab:resolution}, with reduced number of grid points for the parallel velocity $\Nvpar$.
\begin{center}
	\captionsetup{type=table}
	\begin{tabular}{l | ccccc | ccccc | c | cc}
		& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
		\hline
		S6   & 21    & 83    & 16    & 48                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
	\end{tabular}
	\captionof{table}{
		Resolution used in this work: Number of toroidal modes $N_m$, number of radial modes $N_x$, number of grid points along the magnetic field $N_s$,number of parallel velocity grid points $N_{\nu_\parallel}$, number of magnetic moment grid points $N_\mu$, dissipation coefficient used in convection along the magnetic field $D$,the velocity in the dissipation scheme $\nu_d$, dissipation coefficient used in the trapping term $D_{\nu_\parallel}$, damping coefficient of radial modes $D_x$, damping coefficient of toroidal modes $D_y$, order of the scheme used for the zonal mode, maximum poloidal wave vector $k_y\rho$, and maximum radial wave vector $k_x\rho$
	}
	\label{tab:resolution}
\end{center}

>>>>

At the beginning of this work the goal is to estimate the minimal resolution needed to run the simulation without numerical dissipation biasing the physical outcome. Numerical dissipation can therefore result to no formation of zonal flow structures, which cause a permanent turbulent state of the simulation. The goal behind this testing is to reduce \textbf{calculation time} and \textbf{costs} of the simulation. \\
Because of that, the criteria for the best resolution should be:
\begin{enumerate}
	\item[\textbf{(1)}] Subdued turbulence after \textbf{short} time periods
	\item[\textbf{(2)}] Stability for \textbf{long} time periods 
\end{enumerate}
and the following procedure will be applied for verification:
\begin{enumerate}
	\item Reduce only one number of grid points and look if criterias \textbf{(1), (2)} are satisfied
	\item Reduce to known the minimum number of grid points to verify result in general.
\end{enumerate}

@@

Starting from the \enquote{Standard resolution with 6th order (S6)} [Table \ref{tab:resolutionBenchmark}] the first step is to reproduce the result of Ref. \citenum{Peeters2016} in Section IV. Note that, because of selected circular concentric geometry the used inverse background temperature gradient length is $\rlt = 6.0$ instead of $\rlt = 7.0$ which was used in Section IV of Ref. \citenum{Peeters2016} for $s$-$\alpha$ geometry. In Fig. \ref{fig:eflux-ns16-nvpar64-nmu9} the obtained data is similar to the results from Ref. \citenum{Peeters2016} with subdued turbulence after $\sim 3000\,R/\vth$.

\includegraphicsHere{S6_rlt6.0/boxsize1x1/Ns16/Nvpar64/Nmu9/S6_rlt6.0_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux.pdf}{
	Time trace of the heat conduction coefficient $\chi$ for $\rlt = 6.0$ for benchmark.
}{fig:eflux-ns16-nvpar64-nmu9}{}

@@

\includegraphicsHere{Comparison/Gradient-Length/S6_rlt6.0-6.3_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux_comparison.pdf}{
	Time traces for $\rlt = 6.0$ and $\rlt = 6.3$ for benchmark.
}{fig:eflux-gradient-length}{}

@@

\includegraphicsHere{Comparison/Resolution/Nvpar/S6_rlt6.0_boxsize1x1_Ns16_Nvpar16-32-48-64_Nmu9_eflux_comparison.pdf}{
	Time traces for reduced parallel velocity grid points $\Nvpar$.
}{fig:eflux-ns16-nvpar16-32-48-64-nmu9}{}

@@

\includegraphicsHere{Comparison/Resolution/Nmu/S6_rlt6.0_boxsize1x1_Ns16_Nvpar64_Nmu6-9_eflux_comparison.pdf}{
	Time traces for reduced magnetic moment grid points $\Nmu$.
}{fig:eflux-ns16-nvpar64-nmu6-9}{}

@@

\includegraphicsHere{Comparison/Resolution/Nmu/S6_rlt6.0_boxsize1x1_Ns16_Nvpar64_Nmu6-9_eflux_comparison.pdf}{
	Time traces for reduced magnetic moment grid points $\Nmu$.
}{fig:eflux-ns16-nvpar48-nmu6-9}{}

@@

\includegraphicsHere{Comparison/Resolution/Ns/S6_rlt6.0_boxsize1x1_Ns12-16_Nvpar64_Nmu9_eflux_comparison.pdf}{
	Time traces for reduced magnetic field grid points $\Ns$.
}{fig:eflux-ns12-16-nvpar64-nmu9}{}

@@

Together with the results of Chapter \ref{sub:reduceNvpar}, \ref{sub:reduceNmu} and \ref{sub:reduceNs} the final resolution used in the upcoming simulations is displayed in Table \ref{tab:resolution}, with reduced number of grid points for the parallel velocity $\Nvpar$.
\begin{center}
	\captionsetup{type=table}
	\begin{tabular}{l | ccccc | ccccc | c | cc}
		& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
		\hline
		S6   & 21    & 83    & 16    & 48                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
	\end{tabular}
	\captionof{table}{
		Resolution used in this work: Number of toroidal modes $N_m$, number of radial modes $N_x$, number of grid points along the magnetic field $N_s$,number of parallel velocity grid points $N_{\nu_\parallel}$, number of magnetic moment grid points $N_\mu$, dissipation coefficient used in convection along the magnetic field $D$,the velocity in the dissipation scheme $\nu_d$, dissipation coefficient used in the trapping term $D_{\nu_\parallel}$, damping coefficient of radial modes $D_x$, damping coefficient of toroidal modes $D_y$, order of the scheme used for the zonal mode, maximum poloidal wave vector $k_y\rho$, and maximum radial wave vector $k_x\rho$.
	}
	\label{tab:resolution}
\end{center}
